Using the {\tt MovingRegionAlgebra}

### 2006-02-23 Algebras/MovingRegion/Intro/Intro.tex
Continued Intro document.

\newcommand{\secondo}{{\scshape SE\-CON\-DO}}
\newcommand{\mra}{{\tt MovingRegionAlgebra}}
\newcommand{\mr}{{\tt movingregion}}

@@

This document provides information about using the \mra. The
focus is on a very practical perspective, including numerous examples
and screenshots. Basic understanding of \secondo's operation is required
to apply this document.
Section \ref{creating} explains methods to create
\mra\ objects. Section \ref{operations} describes operations on
\mra\ objects including different ways to visualise the results.

@@

@@

>>>>

\newcommand{\secondo}{{\scshape SE\-CON\-DO}}
\newcommand{\mra}{{\tt Moving\-Region\-Algebra}}
\newcommand{\mr}{{\tt movingregion}}

@@

This document provides information about using the \mra. The
focus is on a very practical perspective, including numerous examples
and screenshots. Understanding the operator of \secondo and the moving
regions theory is required to apply this document. Please make sure that
the \mra\ is included in \secondo.

Section \ref{creating} explains methods to create
\mra\ objects. Section \ref{operations} describes operations on
\mra\ objects including different ways to visualise the results.

@@

Please note that segments, which degenerate to a point in the initial or
final instant, are a useful tool to bypass the algebra's requirement that
the segment must keep its orientation through the entire interval of its
unit. If you are facing situations where you cannot meet this requirement,
split the segment into two segments, where the first segment degenerates to
a point in the initial and the second segment degenerates to a point in the
final instant.

During development and initial tests with the \mra, it has been noticed
that there is not much suitable data available which can be used to build
\mr\ objects. As a workaround, Thomas Behr of the Feruniversit"at Hagen
has created the
{\tt Region2MRegion} converter, which applies a list of affine
transformations to a {\tt region} object to construct a \mr\ object.

Lets assume that the following {\tt region} objects exists in \secondo.
\begin{verbatim}
Secondo => query r1;

No specific display function defined. Generic function used.
Type: region
Value: 
(
    (
        (
            (136.0 47.0) 
            (91.0 25.0) 
            (59.0 45.0) 
            (42.0 82.0) 
            (60.0 114.0) 
            (40.0 138.0) 
            (60.0 168.0) 
            (99.0 157.0) 
            (142.0 167.0) 
            (164.0 136.0) 
            (126.0 88.0))))
\end{verbatim}
Use the {\em save} button in the Java GUI to save this object to a file
{\tt r1}.

The {\tt Region2MRegion} converter is located in the directory
\begin{verbatim}
  secondo/Tools/Converter/Region2MRegion
\end{verbatim}
Basic instruction can be found in the {\tt README} file.

Create a file {\tt r1.t} with the following contents.
\begin{verbatim}
(( (translate (100.0 0.0)) )
 ( (translate (100.0 100.0)) )
 ( (translate (100.0 0.0)) ))
\end{verbatim}
This instructs the {\tt Region2MRegion} to create a \mr\ object with
three region units. In the first unit, the region is moved 100 units
to the right. In the second unit, the region is moved 100 units up and
to the right. In the third unit, the region is moved 100 units to the
right again. Each unit has a fixed interval length of six hours and the first
unit's interval starts at {\tt 2000-01-03-00:00:00.000}; the converter does
not allow any other interval specification in the current version.
Lets apply the converter now and put the result into the
file {\tt r1.res}.
\begin{verbatim}
$ ./lintransform r1 r1.t r1.res
Building nested List from File r1 has taken 102 milliseconds
Building nested List from File r1.t has taken 21 milliseconds
processed 11 points
\end{verbatim}
Use the {\em load} button in the Java GUI to load this object. Loading
the file does not create an object in \secondo: Use the {\em store} button
to do this. You may need to rename the object with the {\em rename} button
before this is possible. Figure \ref{creating:r2mr1} shows the resulting
\mr\ object in a number of instants, where two hours are between each
shown instant. Please note the usage of the operators {\tt atinstant} and
{\tt val} to obtain the {\tt region} value of a \mr\ object in a specific
instant.
\begin{figure}
  \begin{center}
    \includegraphics[scale=0.4]{screenshot02.png}
  \end{center}
  \caption{A \mr\ object created with {\tt Region2MRegion}}
  \label{creating:r2mr1}
\end{figure}

@@

\section{Other hints}

precision and rounding errors
